Analyzing Buildlogs Using Programming by Example

### 2019-05-28 paper/paper.tex
move rw points to thesis, write short ones for paper

\section{Introduction}
ci important for sw projects, broken build stops dev process until its fixed, shortening fixing time important to increase dev productivity, to detect underlying failure huge buildlog has to be read, finding relevant information between a lot of lines unimportant for that task, extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity, few existing approaches on specifically that domain, ... our approach ...

\section{Related Work}
\paragraph{CI Research}
google paper, ing \& os java paper, travistorrent
\paragraph{Analyzing Buildlogs}
maven/java paper
\paragraph{Information Extraction}
prose flashextract

TODO put in proper references to the papers youre surely gonna need here

\section{Background}
program synthesis from example, neccessary theoretical stuff

here all the references to prose theoretical papers

>>>>

\section{Introduction}

ci important for sw projects,

broken build stops dev process until its fixed,

shortening fixing time important to increase dev productivity,

to detect underlying failure huge buildlog has to be read, dev has to find relevant information between a lot of lines unimportant for the task,

extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity,

traditional: regexes built for exact information extraction

hard to maintain, regex understanding effort, don't generalize / have to be redone when a bulidlog changes / language or build tool is switched,

... our approach ...,

... paper structure ...

\section{Related Work}

\paragraph{Continious integration and analysis of buildlogs}
se research community started to look into buildlogs as CI becomes a vital part of a modern se process

e.g. Seo at al studying the kinds of errors which lead builds to fail at google and their resolvement time \cite{seo2014programmers}

Vasallo et al compared build failure reasons in java open source software and at one industrial company \cite{vassallo2017a-tale}

Beller et al. conducted a large scale empirical analysis of java and ruby buildlogs from travis ci, found that tests are central to CI and main reason for builds to fail \todo{should I mention a key outcome like this or only what they did?}

Vasallo et al. also build a tool to support developers to find reasons for build breaks fast, analyzes and summarizes relevant parts of a buildlog, links to related stack overflow discussions, they found that \begin{quotation}
	dependency breaks and testing failures seem to be easy to understand
\end{quotation} and a good summary highlighting the locality of the issues seems to be an important factor of fixing time \cite{vassallo2018un-break}

relation to our work: we could support this research by enabling easier data extraction from the analyzed buildlogs, most focus on single/few languages with our tool they could more easily cover multiple ones

\paragraph{Information Extraction from semi-structured data using program synthesis}
Le et al. developed FlashExtract as part of the PROSE Framework, tool to synthesize programs based on a few given examples, extract substrings from semi-structured texts, users can extract multiple fields and structure them with hierarchy and sequence, uses inductive synthesis algorithm to synthesize intended program, eliminates the need for the user to understand structure of entire document or to be able to code

we are applying their library to the domain of buildlogs, using programming by example to take away the need to tediously develop and maintain the regular expressions, traditionally used in information extraction

\section{Background}

\paragraph{semi-structured data}
characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here! -> impact on our work with buildlogs) \cite{abiteboul1997querying}

maybe: reference \cite{smith1997information} and explain approach of first structuring into sections / "contexts" before extracting acutal information. but only if we actually do that and not just always parse the whole log.

program synthesis from example, neccessary theoretical stuff,
here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},
